Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-06-09 mu/article/article.tex
Abstracts of references added in article.abstracts

Using those structures we address a theoretical study of the spin velocity
injection (SVI) by one-photon absorption of linearly polarized light making
emphasis for the particular cases when the spin of electrons is directed along
the the $z$ Cartesian coordinate, perpendicular to the $xy$ plane of the
structure, or for the case when the velocity is directed along the $x$ and $y$
Cartesian direction on the $xy$ plane of the structures.
% 
The SVI ($\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$) is a nonlinear optical
effect that quantifies the velocity at which a PSC moves along the Cartesian
direction $\mathrm{b}$ with the spin of electron polarized along the Cartesian
direction $\mathrm{a}$. One photon absorption of linearly polarized light can
promote a distribution of electrons in $\mathbf{k}$ space regardless the
symmetry of the material resulting in a not net electrical
current. Then, the electrons excited to the conduction bands at
opposite $\mathbf{k}$ points will result in opposite spin polarizations 
producing no net spin injection.\cite{bhatPRL05} If the crystalline structure of
the material is not centrosymmetric the spin polarization injected at a given k
point could not vanish\cite{alvaradoPRL85, schmiedeskampPRL88} and then a PSC
will be produced since the velocities of electrons at opposite $\mathbf{k}$
points are opposite.

>>>>

Using those structures we address a theoretical study of the spin velocity
injection (SVI) by one-photon absorption of linearly polarized light making
emphasis for the particular cases when the spin of electrons is directed along
the the $z$ Cartesian coordinate, perpendicular to the $xy$ plane of the
structure, or for the case when the velocity is directed along the $x$ and $y$
Cartesian direction on the $xy$ plane of the structures.
% 
The SVI ($\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$) is a nonlinear optical
effect that quantifies the velocity at which a PSC moves along the Cartesian
direction $\mathrm{b}$ with the spin of electron polarized along the Cartesian
direction $\mathrm{a}$. One photon absorption of linearly polarized light can
promote a distribution of electrons in $\mathbf{k}$ space regardless the
symmetry of the material resulting in a not net electrical
current. Then, the electrons excited to the conduction bands at
opposite $\mathbf{k}$ points will result in opposite spin polarizations 
producing no net spin injection.\cite{bhatPRL05} If the crystalline structure of
the material is not centrosymmetric the spin polarization injected at a given $
\mathbf{k}$ point could not vanish\cite{alvaradoPRL85, schmiedeskampPRL88} and
then a PSC will be produced since the velocities of electrons at opposite
$\mathbf{k}$ points are opposite.
